P2P-LLM: Collaborative LLM Inference

### 2025-05-05 docs/paper/main.tex
results

\usepackage{jmlr2e}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage[thinc]{esdiff}

@@

@@

>>>>

\usepackage{jmlr2e}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage[thinc]{esdiff}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}

@@

To evaluate the performance, stability, and efficiency of the propose P2P-LLM protocol, I implemented a simulated environment
to model the dynamics of the network.
The simulation explores the relationship between computational resource allocation, price optimization, and network equilibrium under various conditions without requiring the deployment of an actual LLM across distributed hardware.

\subsection{Simulation Framework}
The simulation framework implements a discrete event-based model of the P2P-LLM network, where each event corresponds to a peer action such as joining the network, processing requests, updating prices, or switching layers. The simulation progresses in timesteps, with each timestep representing a fixed duration (e.g., 1 second in simulated time). At each timestep, the following operations are performed:
\begin{enumerate}
	\item Process pending inference requests through the network
	\item Update node prices according to the gradient ascent algorithm (Equation \ref{eq:optim_price})
	\item Periodically, reallocate nodes to new layers (Equation \ref{eq:max})
	\item Create new contracts for peers without a pending contract
	\item Record metrics for analysis
\end{enumerate}
The simulation parameters can be configured to model various network sizes, LLM architectures, and peer behaviors, allowing for comprehensive sensitivity analysis.

\subsection{Network Configuration}

For the simulation, I chose to create a small network, with $n = 28$ total nodes, and a simulated LLM with $m = 4$ layers.
The parameters of the nodes in the network were randomly initialized
where $c_i \in (1,50)$, $l_i \in (1,20)$. All prices are intitially set at $1$. The inital state of the network not optimal with the peers being distributed between the $4$ layers in the configuration $[10, 4, 10, 4]$.
For simplicity, all nodes have an $\alpha$ value of $0.5$ and the $\eta$ used in the iterative pricing function is $1$.

@@

\begin{table}[t]
	\centering
	\caption{P2P-LLM Network Metrics at Different Iteration Steps (Model with 4 Layers, 200 Peers)}
	\label{tab:network-metrics}
	\begin{tabular}{ccccccc}
		\toprule
		\textbf{Iteration} & \textbf{Metric} & \textbf{Layer 1} & \textbf{Layer 2} & \textbf{Layer 3} & \textbf{Layer 4} \\
		\midrule
		\multirow{3}{*}{0}
		                   & Nodes           & 78               & 52               & 34               & 36               \\
		                   & Avg. Price      & 5.42             & 5.28             & 5.87             & 5.31             \\
		\midrule
		\multirow{3}{*}{100}
		                   & Nodes           & 62               & 48               & 43               & 47               \\
		                   & Avg. Price      & 5.89             & 5.96             & 5.72             & 5.68             \\
		\midrule
		\multirow{3}{*}{500}
		                   & Nodes           & 53               & 49               & 50               & 48               \\
		                   & Avg. Price      & 6.12             & 6.08             & 6.10             & 6.05             \\
		\midrule
		\multirow{3}{*}{1000}
		                   & Nodes           & 50               & 50               & 50               & 50               \\
		                   & Avg. Price      & 6.14             & 6.15             & 6.13             & 6.15             \\
		\midrule
		\multirow{3}{*}{5000}
		                   & Nodes           & 50               & 50               & 50               & 50               \\
		                   & Avg. Price      & 6.13             & 6.14             & 6.14             & 6.13             \\
		\bottomrule
	\end{tabular}
\end{table}
